NoTitle

### 2017-06-12 Aplas17/sections/Formalization.tex
proof fix according to mbody change

\subsection{Syntax}

@@

\begin{theorem}[Progress]~\label{theorem_progress}
$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
\begin{enumerate}
\item If $e$ includes $\left(<J>\new{I}\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
    then $ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\item If $e$ includes $\left(<J>\new{I}\right).K::m(\overline{<I_E> e})$ as a subexpression,
    then $ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\item If $e$ includes $\kwsuper.K::m(\overline{<I_E> e})$ as a subexpression,
    then $ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\end{enumerate}
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}

>>>>

\subsection{Syntax} \haoyuan{TODO: syntactic sugar}

@@

\begin{theorem}[Progress]~\label{theorem_progress}
$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
\begin{enumerate}
\item If $e$ includes $\left(<J>\new{I}\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
    then $ \mbody(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\item If $e$ includes $\left(<J>\new{I}\right).K::m(\overline{<I_E> e})$ as a subexpression,
    then $ \mbody(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\item If $e$ includes $\kwsuper.K::m(\overline{<I_E> e})$ as a subexpression,
    then $ \mbody(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\end{enumerate}
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}
